A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-11-11 paper/paper.tex
Cleanup latex comments
Add corresponding author + keywords
Add note about preprint

\documentclass[]{article}
\input{paper.includes.tex}
%\input{paper.definitions.tex}

\title{A flexible integer linear programming formulation for scheduling
	clinician on-call service in hospitals}

\makeatletter
\newcommand{\printfnsymbol}[1]{%
	\textsuperscript{\@fnsymbol{#1}}%
}
\makeatother

\author[a, b]{David Landsman}
\author[a]{Huiting Ma\thanks{Contributed equally to this work.}}
\author[a, c]{Jesse Knight\printfnsymbol{1}}
\author[d]{Kevin Gough}
\author[a, c, d, e]{Sharmistha Mishra}

@@

	\begin{abstract}
		\input{paper.abstract.tex}
	\end{abstract}

	\section{Introduction}\label{sec:introduction}
	\input{paper.intro.tex}
	\section{Problem}\label{sec:problem}
	\input{paper.problem.tex}
	\section{Methods}\label{sec:methods}
	\input{paper.methods.tex}
	\section{Experiments}\label{sec:experiments}
  % JK: not sure the journal requirements, but I would title this section Experiments
  %     since the methods do not introduce any experiments and then its not clear what
  %     results this are refering to.
	\input{paper.experiments.tex}
	\section{Discussion}\label{sec:discussion}
	\input{paper.discussion.tex}
	\section{Acknowledgements}\label{sec:acknowledgements}
	\input{paper.acknowledgements.tex}
	\section{Funding}\label{sec:funding}
	\input{paper.funding.tex}

>>>>

\documentclass[]{article}
\input{paper.includes.tex}

\title{A flexible integer linear programming formulation for scheduling
	clinician on-call service in hospitals}
\date{}

\author[a, b]{David Landsman}
\author[a]{Huiting Ma\thanks{Contributed equally to this work.}}
\author[a, c]{Jesse Knight\printfnsymbol{1}}
\author[d]{Kevin Gough}
\author[a, c, d, e]{Sharmistha Mishra\thanks{Corresponding author (\texttt{sharmistha.mishra@utoronto.ca})}}

@@

	\begin{abstract}
		\input{paper.abstract.tex}
	\end{abstract}
	\keywords{Clinician scheduling, Integer linear programming, Exact method, Optimization, Clinician requests}
	\blfootnote{Preprint submitted to arXiv: \href{https://arxiv.org/abs/1910.08526}{https://arxiv.org/abs/1910.08526}}

	\section{Introduction}\label{sec:introduction}
	\input{paper.intro.tex}
	\section{Problem}\label{sec:problem}
	\input{paper.problem.tex}
	\section{Methods}\label{sec:methods}
	\input{paper.methods.tex}
	\section{Experiments}\label{sec:experiments}
	\input{paper.experiments.tex}
	\section{Discussion}\label{sec:discussion}
	\input{paper.discussion.tex}
	\section{Acknowledgements}\label{sec:acknowledgements}
	\input{paper.acknowledgements.tex}
	\section{Funding}\label{sec:funding}
	\input{paper.funding.tex}
